---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pourquoi

**Why settle for one noisy answer when you can vote & verify?**

Add robust step-by-step reasoning to any base language model. Generate diverse reasoning traces, vote on the consensus, and verify with the same LLM or via a separate low-cost LLM.   

pourquoi uses Verified Self-Consistency (VSC), a minimal ensemble technique: generate diverse traces with a base model for reasoning, normalize answers for consensus voting, then verify with a final LLM verifier.


```{r}
library(pourquoi)
```


```{r}
prompt <- "how do i say why in French?"

pourquoi::why(
  prompt = prompt,
  reasoner = "ollama/gemma3:4b",
  verifier = "ollama/qwen3:0.6b",
  n_traces = 3
)

```


```{r}
prompt <- "how many r's are in the word Strawberry?"

pourquoi::why(
  prompt = prompt,
  reasoner = "ollama/ministral-3:8b",
  verifier = "ollama/ministral-3:3b",
  n_traces = 5
)

```